### 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@08ded612bd8bda0c46eddd995b9850c9683d8208 🚀

\textbf{Acknowledgements:} This work was supported by funding to the
Viral Emergence Research Initiative (VERENA) consortium including NSF
BII 2021909 and a grant from Institut de Valorisation des Données
(IVADO), by the NSERC Discovery Grants and Discovery Acceleration
Supplement programs, and by a donation from the Courtois Foundation.
Benchmarking of this package on distributed systems was enabled by
support provided by Calcul Québec (\texttt{www.calculquebec.ca}) and
Compute Canada (\texttt{www.computecanada.ca}). TP wrote the initial
code, TP and CJC contributed to API design, and all authors contributed
to functionalities and usability testing.

>>>>

\textbf{Acknowledgements:} This work was supported by funding to the
Viral Emergence Research Initiative (VERENA) consortium including NSF
BII 2021909 and 2213854 and a grant from Institut de Valorisation des
Données (IVADO), by the NSERC Discovery Grants and Discovery
Acceleration Supplement programs, and by a donation from the Courtois
Foundation. Benchmarking of this package on distributed systems was
enabled by support provided by Calcul Québec
(\texttt{www.calculquebec.ca}) and Compute Canada
(\texttt{www.computecanada.ca}). TP wrote the initial code, TP and CJC
contributed to API design, and all authors contributed to
functionalities and usability testing.
